---
title: "Exploratory Analysis of Current Russell 2000"
author: "Jacob Mason"
date: "2025-01-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}


library(tidyverse)

library(rvest)

library(readxl)

library(quantmod)

```



THe below is code to pull in the stock prices for all of the Russell 2000 component stocks on 1_23_2025 at approximately 2 pm EST.   I do not have excel installed on this computer so the output is being pulled from a txt file.  

The output generated clearly shows that the leading digits of the Russell 2000 component prices follow the Benfords law distrobution quite closely. 

```{r}

x <- read.delim("C://Users//user//Desktop//All Russell 2000 stock price 1_23_2025.txt", header = TRUE)

x |> select(Company) |> filter(str_detect(Company,'\\$')) |> mutate(leading_digit = str_sub(Company,2,2)) |> count(leading_digit) |> mutate(percentage = n/sum(n) *100) |> ggplot(aes(x = leading_digit, y = n)) + 
  geom_bar(stat = "identity", fill = "skyblue") +
  geom_text(aes(label= paste0(round(percentage,1),"%")),vjust = -0.5)+
  labs(
    title = "Leading Digit Distrobution in Russell 2000 1_23_2025",
    x= "Leading Digit",
    y= "Frequency"
  ) +
  theme_minimal()



print(x)

```



THis next set of code is used to pull in the list of all the components of the Russell 2000 index from a download that can be found on the IWM website located here:
https://www.ishares.com/us/products/239710/ishares-russell-2000-etf#Holdings

I had to use this as a proxy for the actual make up of the russell 2000.  It is difficult to find that data in a usable format. 
```{r}

List_of_Russel_Ticker_Symbols_Path <- "C:/Users/user/Desktop/Benfords Law/IWM_holdings (Russell 2000 Proxy).txt"

Russell_Ticker <- read_csv(List_of_Russel_Ticker_Symbols_Path)

Just_Ticker <- Russell_Ticker |> select(Ticker)

print(Just_Ticker)

```

Now I will take those ticker symbols and pull current price data from Yahoo.com.

```{r}

tickers <- c("SFM", "MSFT", "GOOGL", "AMZN", "META")

print(tickers)

stock_data <- data.frame()


for (ticker in Just_Ticker$Ticker) {
  tryCatch({
    # Get stock data for the ticker
    stock <- getQuote(ticker, src = "yahoo")
    
    # Extract relevant data
    stock_info <- data.frame(
      company = ticker, 
      price = stock$Last
    )
    
    # Append to the main dataset
    stock_data <- bind_rows(stock_data, stock_info)
  }, error = function(e) {
    message(paste("Error fetching data for ticker:", ticker))
  })
}

# Print the final dataset
print(stock_data)

```


This is to check the data pulled from Yahoo to make sure it is also following the Benfords Law distribution. 
```{r}

stock_data |> select(price) |> mutate(leading_digit = str_sub(price,1,1)) |> count(leading_digit) |> mutate(percentage = n/sum(n) *100) |> ggplot(aes(x = leading_digit, y = n)) + 
  geom_bar(stat = "identity", fill = "skyblue") +
  geom_text(aes(label= paste0(round(percentage,1),"%")),vjust = -0.5)+
  labs(
    title = "Leading Digit Distrobution in Russell 2000 1_24_2025",
    x= "Leading Digit",
    y= "Frequency"
  ) +
  theme_minimal()



```

The next piece of code will select only the tickers and prices of stocks with leading digit 9s
```{r}

Only_9s <- stock_data |> filter(grepl("^9", price))

print(Only_9s)

Only_9s |> filter(price < 250) |> ggplot(aes(x=price)) +
  geom_histogram(binwidth = 1)


```

now I want to save stock data as data with date of 1/24/2025.

```{r}

Rusell_2000_Prices_1_24_2025 <- stock_data

```



```{r}

print(Jan_24_2025)



```


